---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
library(sf)
library(mapview)
library(suncalc)
library(googledrive)
library(there)
library(colorspace)
```

```{r}
altitude_locations <- st_read("altitude_locs_3D_geoid_terrain_height_8_25_22.shp") %>%
  st_drop_geometry() %>%
  mutate(time = NULL,
         POINT_X = NULL,
         POINT_Y = NULL,
         POINT_Z = NULL,
         POINT_M = NULL,
         Field1 = NULL,
         elev_geoid = as.numeric(elev_geoid)) %>%
  rename(terrain_height = RASTERVALU,
         height_above_ellipsoid = height_abo) %>%
  mutate(alt_hat = elev_geoid - terrain_height)

prior_alt_locations <- read.csv("altitude_locs_3D.csv") %>%
  dplyr::select(ID, time, lon, lat)
  
altitude_locations <- altitude_locations %>%
   left_join(prior_alt_locations)

altitude_locations$time <- altitude_locations$time %>% ymd_hms() 
```

Distinguishing between day and night locations (between sunrise and sunset)
```{r}
altitude_locations %>%
  dplyr::transmute(date = as.Date(time), lat = lat, lon = lon) %>%
  getSunlightTimes(data = .) %>%
  pull(sunrise) -> 
  altitude_locations$sunrise

altitude_locations %>%
  dplyr::transmute(date = as.Date(time), lat = lat, lon = lon) %>%
  getSunlightTimes(data = .) %>%
  pull(sunset) -> 
  altitude_locations$sunset

altitude_locations %>%
  mutate(day_night = if_else(time > sunrise & time < sunset, "Day", "Night")) ->
  altitude_locations
```

Show height above terrain for all elevation locations. 13 NAs in here; remember to embed time as text next time
```{r}
altitude_locations %>%
  #filter(day_night == "Day") %>%
  ggplot(aes(x = day_night, y = alt_hat)) +
  geom_boxplot() +
  EnvStats::stat_n_text()
```

Show for 2D vs 3D locations, and remove 2D locations
```{r}
altitude_locations %>%
  filter(day_night == "Day") %>%
  ggplot(aes(x = fix, y = alt_hat)) +
  geom_boxplot() +
  EnvStats::stat_n_text()

altitude_locations %>%
  filter(fix == "3D") ->
  altitude_locations_3D
```

```{r}
altitude_locations_3D %>%
  ggplot(aes(x = day_night, y = alt_hat)) +
  geom_boxplot() +
  EnvStats::stat_n_text() + 
  theme_bw()
```

```{r}
altitude_locations_3D %>%
  filter(day_night == "Day") %>%
  pull(alt_hat) %>%
  quantile(c(.99))

#Calling anything at night that is higher than 115.3186 m a flight location
# 8/25/22 new boundary is 107.5387 
```

Breaking night flight locations out by individual, age, and sex
```{r}
night_flight_locations <- altitude_locations_3D %>%
  filter(day_night == "Night") %>%
  rename(`Movebank ID` = ID) %>%
  filter(alt_hat > 107.5387)

as_id("https://drive.google.com/file/d/19JA5OztH3hS4MPfVnH5zswDxSSLcWxL3/view?usp=sharing") %>%
  drive_download(path = here_file("Data", "Google_drive_downloads","capture_sheet.xlsx"), overwrite = TRUE)

capture_sheet <- readxl::read_excel(here_file("Data", "Google_drive_downloads","capture_sheet.xlsx"), col_types = c("text", "text", "date", "numeric", "numeric", "numeric", "numeric", "text", "text", "text", "text", "text", "text", "numeric", "numeric", "numeric", "numeric", "numeric", "text", "text", "text", "text")) %>%
  mutate(`Argos ID` = as.character(`Argos ID`))

capture_sheet %>%
  dplyr::select(`Movebank ID`, Sex, Age) %>%
  right_join(night_flight_locations) ->
  night_flight_locations


night_flight_locations$`Movebank ID` %>% unique() %>% length() #50 individuals #8/25/2022 72 individuals

#locations broken out by age and sex
night_flight_locations %>%
  group_by(Sex, Age) %>%
  tally() %>%
  View()

#individuals broken out by age and sex
night_flight_locations %>%
  dplyr::select(`Movebank ID`, Sex, Age) %>%
  distinct() %>%
  group_by(Sex, Age) %>%
  tally() %>%
  View()

```

Attaching season so that I can further break out by season
```{r}
night_flight_locations %>%
  mutate(month_day = as.numeric(paste0(month(time), "." , day(time)))) %>%
  mutate(season = ifelse(month_day > 9 | month_day < 2, "Fall", "Breeding")) %>%
  mutate(season = ifelse(month_day > 2 & month_day < 6, "Spring", season)) ->
  night_flight_locations

#locations broken out by age and sex
night_flight_locations %>%
  #filter(season == "Spring") %>%
  group_by(Sex, Age, season) %>%
  tally() %>%
  View()

#individuals broken out by age and sex
night_flight_locations %>%
  #filter(season == "Spring") %>%
  dplyr::select(`Movebank ID`, Sex, Age, season) %>%
  distinct() %>%
  group_by(Sex, Age) %>%
  tally() %>%
  View()
```

Running the histogram (by season this time)
```{r}
night_flight_locations %>%
  filter(season != "Breeding") %>% 
  ggplot(aes(x = season, y = alt_hat)) +
  geom_boxplot() +
  theme_bw() +
  xlab("Season") +
  ylab("Altitude (m)") +
  EnvStats::stat_n_text()

ggsave("altitude_by_season_revised_8_25_22.png", width = 6, height = 5)
```


saving night flight locations as a shapefile
```{r}
st_write(night_flight_locations, "night_flight_locations_9_1_22.shp")
```

Barplot with the # of night flight locations in each season broken out by age and sex
```{r}
night_flight_locations %>%
  mutate(Age = recode(Age, "AHY" = "Adult", "ASY" = "Adult", "HY" = "Young", "SY" = "Young")) %>%
  group_by(Sex, Age, season) %>%
  tally() %>%
  mutate(season = recode(season, "Breeding" = "Summer")) %>%
  ggplot(aes(x = Sex, fill = Age, y = n)) +
  geom_bar(position = "dodge", color = "black", stat = "identity") +
  theme_bw() +
  facet_wrap(vars(season)) +
  ylab("Number of locations") +
  scale_fill_manual(values = diverge_hcl(2, c = 130))

ggsave("num_locs_age_sex_season_2022.png", width = 7, height = 5)
```

