---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

```{r}
original_results <- readRDS(here("modeling", "results", "lnorm_original.rds"))
```

Median
```{r}
plan(multisession)

median_draws <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws %>% 
  unlist() %>% 
  median() #224.469

median_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [201.27, 251.27]

median_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [148.15, 295.01]
```

Mean
```{r}
plan(multisession)

mean_draws <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws %>% 
  unlist() %>% 
  median() #361.0677

mean_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [333.12, 386.44]

mean_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [284.74, 444.20]
```

Standard deviation
```{r}
plan(multisession)

sd_draws <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws %>% 
  unlist() %>% 
  median() # 448.8329

sd_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [365.05, 484.56]

sd_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [293.69, 685.57]
```

Skewness
```{r}
plan(multisession)

skew_draws <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws %>% 
  unlist() %>% 
  median() # 5.097035

skew_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [3.70, 5.57]

skew_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.67, 10.65]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
plan(multisession)

pct_below_radar_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold %>% 
  unlist() %>% 
  median() #0.35145

pct_below_radar_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.29, 0.40]

pct_below_radar_threshold %>% 
  unlist() %>% 
  hdi(0.95) #95% HDI: [0.21, 0.50]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
plan(multisession)

pct_below_building_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold %>% 
  unlist() %>% 
  median() #0.0538

pct_below_building_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.02, 0.06]

pct_below_building_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.15]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
plan(multisession)

pct_below_comm_tower_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  median() #0.6238

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.59, 0.66]

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.52, 0.73]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
plan(multisession)

pct_below_wind_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(original_results, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold %>% 
  unlist() %>% 
  median() #0.3486

pct_below_wind_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.32, 0.39]

pct_below_wind_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.24, 0.44]
```
