---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Fall is index 1, spring 2

```{r}
season_results <- readRDS(here("modeling", "results", "lnorm_season.rds"))
```

Median
```{r}
#fall
plan(multisession)

median_draws_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_fall %>% 
  unlist() %>% 
  median() #241.6429

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [222.55, 258.75]

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [187.89, 295.78]

# spring
plan(multisession)

median_draws_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_spring %>% 
  unlist() %>% 
  median() #294.8802

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [266.61, 318.49]

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [219.75, 375.58]
```

Mean
```{r}
#fall
plan(multisession)

mean_draws_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_fall %>% 
  unlist() %>% 
  median() #337.7761

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [305.67, 357.53]

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [267.02, 422.94]

#spring
plan(multisession)

mean_draws_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_spring %>% 
  unlist() %>% 
  median() #444.0485

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [398.31, 476.48]

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [333.05, 577.71]
```

Standard deviation
```{r}
plan(multisession)

sd_draws_fall <- future_map2(.x = rstan::extract(season_results, pars = c("mu_alt_fall"))[[1]], 
            .y = rstan::extract(season_results, pars = c("sigma_alt_fall"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_fall %>% 
  unlist() %>% 
  median() #327.9796

sd_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [262.50, 352.54]

sd_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [209.94, 504.04]

plan(multisession)

sd_draws_spring <- future_map2(.x = rstan::extract(season_results, pars = c("mu_alt_spring"))[[1]], 
            .y = rstan::extract(season_results, pars = c("sigma_alt_spring"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_spring %>% 
  unlist() %>% 
  median() #491.2334

sd_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [379.91, 534.56]

sd_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [291.90, 824.63]
```

Skewness
```{r}
plan(multisession)

skew_draws_fall <- future_map2(.x = rstan::extract(season_results, pars = c("mu_alt_fall"))[[1]], 
            .y = rstan::extract(season_results, pars = c("sigma_alt_fall"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_fall %>% 
  unlist() %>% 
  median() #3.646246

skew_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [2.86, 3.90]

skew_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.33, 6.24]

plan(multisession)

skew_draws_spring <- future_map2(.x = rstan::extract(season_results, pars = c("mu_alt_spring"))[[1]], 
            .y = rstan::extract(season_results, pars = c("sigma_alt_spring"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_spring %>% 
  unlist() %>% 
  median() #4.344244

skew_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [3.27, 4.70]

skew_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.48, 8.38]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#fall
plan(multisession)

pct_below_radar_threshold_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  median() #0.2926

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.33]

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.19, 0.40]

#spring
plan(multisession)

pct_below_radar_threshold_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  median() #0.2357

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.20, 0.27]

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.35]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#fall
plan(multisession)

pct_below_building_threshold_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  median() #0.0223

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.03]

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.06]

#spring
plan(multisession)

pct_below_building_threshold_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  median() #0.0201

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.02]

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.06]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#fall
plan(multisession)

pct_below_comm_tower_threshold_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  median() #0.6124

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.58, 0.65]

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.51, 0.71]

#spring
plan(multisession)

pct_below_comm_tower_threshold_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  median() #0.515

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.48, 0.56]

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.40, 0.63]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#fall
plan(multisession)

pct_below_wind_threshold_fall <- future_map2(.x = rstan::extract(season_results, "mu_alt_fall")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  median() #0.3088

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.28, 0.34]

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.22, 0.41]

#spring
plan(multisession)

pct_below_wind_threshold_spring <- future_map2(.x = rstan::extract(season_results, "mu_alt_spring")[[1]], 
            .y = rstan::extract(season_results, "sigma_alt_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  median() #0.248

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.28]

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.35]
```

Quantify the likelihood that one seasonal mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_spring) > unlist(mean_draws_fall))*100/length(unlist(mean_draws_spring))
#93.69667% probability that the spring mean is higher than the fall mean
```

