---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Adult is index 1, Juvenile 2
```{r}
age_results <- readRDS(here("modeling", "results", "lnorm_age.rds"))
```

Median
```{r}
# adult
plan(multisession)

median_draws_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_adult %>% 
  unlist() %>% 
  median() #291.4735

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [264.96, 316.38]

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [218.23, 373.99]

# juv
plan(multisession)

median_draws_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_juv %>% 
  unlist() %>% 
  median() #266.0887

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [247.08, 286.09]

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [210.44, 324.63]
```

Mean
```{r}
# adult
plan(multisession)

mean_draws_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_adult %>% 
  unlist() %>% 
  median() #431.222

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [376.85, 459.42]

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [316.56, 581.20]

# juv
plan(multisession)

mean_draws_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_juv %>% 
  unlist() %>% 
  median() #370.8597

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [337.28, 393.26]

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [294.91, 465.26]
```

Standard deviation
```{r}
plan(multisession)

sd_draws_adult <- future_map2(.x = rstan::extract(age_results, pars = c("mu_alt_adult"))[[1]], 
            .y = rstan::extract(age_results, pars = c("sigma_alt_adult"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_adult %>% 
  unlist() %>% 
  median() #464.5481

sd_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [349.89, 508.57]

sd_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [261.81, 804.93]

plan(multisession)

sd_draws_juv <- future_map2(.x = rstan::extract(age_results, pars = c("mu_alt_juv"))[[1]], 
            .y = rstan::extract(age_results, pars = c("sigma_alt_juv"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_juv %>% 
  unlist() %>% 
  median() #358.4397

sd_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [291.99, 389.74]

sd_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [232.64, 545.77]
```

Skewness
```{r}
plan(multisession)

skew_draws_adult <- future_map2(.x = rstan::extract(age_results, pars = c("mu_alt_adult"))[[1]], 
            .y = rstan::extract(age_results, pars = c("sigma_alt_adult"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_adult %>% 
  unlist() %>% 
  median() #4.188694

skew_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [3.20, 4.59]

skew_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.33, 7.86]

plan(multisession)

skew_draws_juv <- future_map2(.x = rstan::extract(age_results, pars = c("mu_alt_juv"))[[1]], 
            .y = rstan::extract(age_results, pars = c("sigma_alt_juv"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_juv %>% 
  unlist() %>% 
  median() #3.627106

skew_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [2.91, 3.93]

skew_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.31, 6.12]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
# adult
plan(multisession)

pct_below_radar_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  median() #0.2359

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.20, 0.27]

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.35]

# juv
plan(multisession)

pct_below_radar_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  median() #0.2535

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.22, 0.29]

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.36]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
# adult
plan(multisession)

pct_below_building_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  median() #0.0189

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.02]

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.06]

# juv
plan(multisession)

pct_below_building_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  median() #0.0166

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.02]

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.05]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
# adult
plan(multisession)

pct_below_comm_tower_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  median() #0.5205

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.48, 0.56]

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.41, 0.64]

# juv
plan(multisession)

pct_below_comm_tower_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  median() #0.5668

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.53, 0.60]

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.46, 0.66]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
# adult
plan(multisession)

pct_below_wind_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  median() #0.2489

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.28]

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.35]

# juv
plan(multisession)

pct_below_wind_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  median() #0.2704

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.23, 0.30]

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.18, 0.36]
```

Quantify the likelihood that one age mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_adult) > unlist(mean_draws_juv))*100/length(unlist(mean_draws_adult))
#79.06333% probability that the adult mean is higher than the juvenile mean
```