---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Adult is index 1, Juvenile 2
```{r}
age_results <- readRDS(here("modeling", "results", "lnorm_age.rds"))
```

Median
```{r}
# adult
plan(multisession)

median_draws_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_adult %>% 
  unlist() %>% 
  median() #278.4478

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [242.15, 313.73]

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [170.66, 380.69]

# juv
plan(multisession)

median_draws_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_juv %>% 
  unlist() %>% 
  median() #249.2478

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [222.51, 283.22]

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [163.79, 335.88]
```

Mean
```{r}
# adult
plan(multisession)

mean_draws_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_adult %>% 
  unlist() %>% 
  median() #434.9942

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [375.18, 468.52]

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [304.85, 600.81]

# juv
plan(multisession)

mean_draws_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_juv %>% 
  unlist() %>% 
  median() #368.5115

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [332.00, 398.98]

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [276.97, 476.57]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
# adult
plan(multisession)

pct_below_radar_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  median() #0.2666

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.20, 0.32]

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.11, 0.45]

# juv
plan(multisession)

pct_below_radar_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  median() #0.2944

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.22, 0.34]

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.47]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
# adult
plan(multisession)

pct_below_building_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  median() #0.0294

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.00, 0.03]

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.12]

# juv
plan(multisession)

pct_below_building_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  median() #0.029

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.00, 0.03]

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.12]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
# adult
plan(multisession)

pct_below_comm_tower_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  median() #0.5389

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.48, 0.59]

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.39, 0.69]

# juv
plan(multisession)

pct_below_comm_tower_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  median() #0.5911

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.54, 0.64]

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.46, 0.72]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
# adult
plan(multisession)

pct_below_wind_threshold_adult <- future_map2(.x = rstan::extract(age_results, "mu_alt_adult")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  median() #0.2738

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.22, 0.32]

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.40]

# juv
plan(multisession)

pct_below_wind_threshold_juv <- future_map2(.x = rstan::extract(age_results, "mu_alt_juv")[[1]], 
            .y = rstan::extract(age_results, "sigma_alt_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  median() #0.3051

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.25, 0.36]

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.17, 0.43]
```

Quantify the likelihood that one age mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_adult) > unlist(mean_draws_juv))*100/length(unlist(mean_draws_adult))
#78.58% probability that the adult mean is higher than the juvenile mean
```