---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

male is index 1, female 2

```{r}
sex_results <- readRDS(here("modeling", "results", "lnorm_sex.rds"))
```

Median
```{r}
#male
plan(multisession)

median_draws_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_male %>% 
  unlist() %>% 
  median() #288.9157

median_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [265.03, 309.35]

median_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [224.78, 355.80]

# female
plan(multisession)

median_draws_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_female %>% 
  unlist() %>% 
  median() #247.3819

median_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [227.72, 270.94]

median_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [184.09, 310.66]
```

Mean
```{r}
#male
plan(multisession)

mean_draws_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_male %>% 
  unlist() %>% 
  median() #416.6394

mean_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [378.64, 445.91]

mean_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [325.54, 531.51]

#female
plan(multisession)

mean_draws_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_female %>% 
  unlist() %>% 
  median() #351.7236

mean_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [315.69, 376.33]

mean_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [269.90, 456.22]
```

Standard deviation
```{r}
plan(multisession)

sd_draws_male <- future_map2(.x = rstan::extract(sex_results, pars = c("mu_alt_male"))[[1]], 
            .y = rstan::extract(sex_results, pars = c("sigma_alt_male"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_male %>% 
  unlist() %>% 
  median() #428.8741

sd_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [337.33, 460.57]

sd_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [268.72, 674.27]

plan(multisession)

sd_draws_female <- future_map2(.x = rstan::extract(sex_results, pars = c("mu_alt_female"))[[1]], 
            .y = rstan::extract(sex_results, pars = c("sigma_alt_female"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

plan(sequential)

sd_draws_female %>% 
  unlist() %>% 
  median() #351.8347

sd_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [275.69, 381.26]

sd_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [210.74, 567.11]
```

Skewness
```{r}
plan(multisession)

skew_draws_male <- future_map2(.x = rstan::extract(sex_results, pars = c("mu_alt_male"))[[1]], 
            .y = rstan::extract(sex_results, pars = c("sigma_alt_male"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_male %>% 
  unlist() %>% 
  median() #3.934689

skew_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [3.08, 4.24]

skew_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.40, 6.95]

plan(multisession)

skew_draws_female <- future_map2(.x = rstan::extract(sex_results, pars = c("mu_alt_female"))[[1]], 
            .y = rstan::extract(sex_results, pars = c("sigma_alt_female"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

plan(sequential)

skew_draws_female %>% 
  unlist() %>% 
  median() #3.799714

skew_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [2.89, 4.06]

skew_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.20, 6.77]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that male below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#male
plan(multisession)

pct_below_radar_threshold_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  median() #0.232

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.19, 0.26]

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.14, 0.34]

#female
plan(multisession)

pct_below_radar_threshold_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  median() #0.2875

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.24, 0.32]

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.17, 0.41]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#male
plan(multisession)

pct_below_building_threshold_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_male %>% 
  unlist() %>% 
  median() #0.0165

pct_below_building_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.02]

pct_below_building_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.05]

#female
plan(multisession)

pct_below_building_threshold_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_female %>% 
  unlist() %>% 
  median() #0.0232

pct_below_building_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.01, 0.03]

pct_below_building_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.00, 0.07]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#male
plan(multisession)

pct_below_comm_tower_threshold_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  median() #0.5253

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.49, 0.56]

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.42, 0.63]

#female
plan(multisession)

pct_below_comm_tower_threshold_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  median() #0.5992

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.57, 0.64]

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.49, 0.71]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#male
plan(multisession)

pct_below_wind_threshold_male <- future_map2(.x = rstan::extract(sex_results, "mu_alt_male")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  median() #0.2467

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.27]

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.16, 0.34]

#female
plan(multisession)

pct_below_wind_threshold_female <- future_map2(.x = rstan::extract(sex_results, "mu_alt_female")[[1]], 
            .y = rstan::extract(sex_results, "sigma_alt_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  median() #0.3021

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.34]

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.20, 0.41]
```

Quantify the likelihood that one sex's mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_male) > unlist(mean_draws_female))*100/length(unlist(mean_draws_male))
#82.39333 probability that the female mean is higher than the male mean
```

