---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

male is index 1, female 2

```{r}
sex_results <- readRDS(here("bayesian_modeling", "gamma_sex_stan.rds"))
```

Mode
```{r}
# mode (calculated from samples)
# male
mode_draws_male <- ((rstan::extract(sex_results, "shape_male")[[1]] - 1)/rstan::extract(sex_results, "rate_male")[[1]])*2183.475

median(mode_draws_male)
#56.42664

hdi(mode_draws_male, ci = 0.95)
#95% HDI: [-139.53, 234.72]

#female
mode_draws_female <- ((rstan::extract(sex_results, "shape_female")[[1]] - 1)/rstan::extract(sex_results, "rate_female")[[1]])*2183.475

median(mode_draws_female)
#79.7429

hdi(mode_draws_female, ci = 0.95)
#95% HDI: [-62.29, 204.92]
```

Median
```{r}
#male
plan(multisession)

median_draws_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_male %>% 
  unlist() %>% 
  median() #287.0442

median_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [247.60, 320.87]

median_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [181.83, 394.41]

# female
plan(multisession)

median_draws_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_female %>% 
  unlist() %>% 
  median() #252.9734

median_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [226.29, 283.31]

median_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [169.75, 334.93]
```

Mean
```{r}
#male
plan(multisession)

mean_draws_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_male %>% 
  unlist() %>% 
  median() #392.2709

mean_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [357.32, 426.56]

mean_draws_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [292.33, 495.90]

#female
plan(multisession)

mean_draws_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_female %>% 
  unlist() %>% 
  median() #333.4846

mean_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [302.30, 358.91]

mean_draws_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [255.61, 420.61]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that male below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#male
plan(multisession)

pct_below_radar_threshold_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  median() #0.2948

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [0.24, 0.35]

pct_below_radar_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.45]

#female
plan(multisession)

pct_below_radar_threshold_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  median() #0.3195

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.27, 0.37]

pct_below_radar_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.18, 0.46]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#male
plan(multisession)

pct_below_building_threshold_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_male %>% 
  unlist() %>% 
  median() #0.0861

pct_below_building_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.01, 0.20]

#female
plan(multisession)

pct_below_building_threshold_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_female %>% 
  unlist() %>% 
  median() #0.0834

pct_below_building_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.02, 0.18]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#male
plan(multisession)

pct_below_comm_tower_threshold_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  median() #0.5237

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.48, 0.57]

pct_below_comm_tower_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.38, 0.65]

#female
plan(multisession)

pct_below_comm_tower_threshold_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  median() #0.5783

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.54, 0.63]

pct_below_comm_tower_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.45, 0.70]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#male
plan(multisession)

pct_below_wind_threshold_male <- future_map2(.x = rstan::extract(sex_results, "shape_male")[[1]], 
            .y = rstan::extract(sex_results, "rate_male")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  median() #0.2514

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.23, 0.28]

pct_below_wind_threshold_male %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.16, 0.32]

#female
plan(multisession)

pct_below_wind_threshold_female <- future_map2(.x = rstan::extract(sex_results, "shape_female")[[1]], 
            .y = rstan::extract(sex_results, "rate_female")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  median() #0.28195

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.31]

pct_below_wind_threshold_female %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.20, 0.36]
```

Quantify the likelihood that one sexal mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_male) > unlist(mean_draws_female))*100/length(unlist(mean_draws_male))
#81.12% probability that the female mean is higher than the male mean
```

