---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Fall is index 1, spring 2

```{r}
season_results <- readRDS(here("bayesian_modeling", "gamma_season.rds"))
```

Mode
```{r}
# mode (calculated from samples)
# fall
mode_draws_fall <- ((season_results$sims.list$shape_flight[,1] - 1)/season_results$sims.list$rate_flight[,1])*2183.475

median(mode_draws_fall)
#33.08025

hdi(mode_draws_fall, ci = 0.95)
#95% HDI: [-117.43, 168.46]

#spring
mode_draws_spring <- ((season_results$sims.list$shape_flight[,2] - 1)/season_results$sims.list$rate_flight[,2])*2183.475

median(mode_draws_spring)
#87.06981

hdi(mode_draws_spring, ci = 0.95)
#95% HDI: [-105.58, 252.48]
```

Median
```{r}
#fall
plan(multisession)

median_draws_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_fall %>% 
  unlist() %>% 
  median() # 223.8051

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [192.93, 248.95]

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) # 95% HDI: [144.60, 307.80]

# spring
plan(multisession)

median_draws_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_spring %>% 
  unlist() %>% 
  median() #319.5573

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [282.82, 355.78]

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [215.01, 425.94]
```

Mean
```{r}
#fall
plan(multisession)

mean_draws_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_fall %>% 
  unlist() %>% 
  median() #310.0161

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [279.42, 333.61]

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [234.80, 393.42]

#spring
plan(multisession)

mean_draws_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_spring %>% 
  unlist() %>% 
  median() #426.9676

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [391.84, 462.87]

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [323.71, 536.31]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#fall
plan(multisession)

pct_below_radar_threshold_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  median() #0.3728

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [0.32, 0.42]

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.23, 0.51]

#spring
plan(multisession)

pct_below_radar_threshold_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  median() #0.2569

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.30]

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.40]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#fall
plan(multisession)

pct_below_building_threshold_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  median() #0.1191

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.07, 0.15]

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.03, 0.23]

#spring
plan(multisession)

pct_below_building_threshold_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  median() #0.0678

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.03, 0.08]

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.01, 0.16]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#fall
plan(multisession)

pct_below_comm_tower_threshold_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  median() #0.6194

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.58, 0.66]

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.50, 0.73]

#spring
plan(multisession)

pct_below_comm_tower_threshold_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  median() #0.4815

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.44, 0.53]

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.35, 0.62]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#fall
plan(multisession)

pct_below_wind_threshold_fall <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  median() #0.3064

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.29, 0.33]

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.23, 0.37]

#spring
plan(multisession)

pct_below_wind_threshold_spring <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  median() #0.2271

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.20, 0.26]

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.30]
```

Quantify the likelihood that one seasonal mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_spring) > unlist(mean_draws_fall))*100/length(unlist(mean_draws_spring))
#95.60882% probability that the spring mean is higher than the fall mean
```

