---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

```{r}
original_results <- readRDS(here("bayesian_modeling", "gamma_original_stan2.rds"))
```

Mode
```{r}
# mode (calculated from samples)
mode_draws <- ((rstan::extract(original_results, pars = c("shape"))[[1]] - 1)/rstan::extract(original_results, pars = c("rate"))[[1]])*2183.475

median(mode_draws)
#38.98425

hdi(mode_draws, ci = 0.95)
# 95% HDI: [-88.32, 156.58]
```

Median
```{r}
plan(multisession)

median_draws <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws %>% 
  unlist() %>% 
  median() #261.6436 new 217.5314

median_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [236.42, 283.97] new 50% HDI: [179.69, 264.29]

median_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [193.53, 330.54] new 95% HDI: [85.87, 331.73]
```

Mean
```{r}
plan(multisession)

mean_draws <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws %>% 
  unlist() %>% 
  median() #361.9758 new 329.2261

mean_draws %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [338.23, 383.89] new 50% HDI: [298.63, 368.49]

mean_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [298.66, 433.16] new 95% HDI: [214.54, 426.70]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
plan(multisession)

pct_below_radar_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold %>% 
  unlist() %>% 
  median() #0.3253 new 0.3972

pct_below_radar_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.29, 0.36] new 50% HDI: [0.31, 0.45]

pct_below_radar_threshold %>% 
  unlist() %>% 
  hdi(0.95) #95% HDI: [0.22, 0.43] new 95% HDI: [0.22, 0.62]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
plan(multisession)

pct_below_building_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold %>% 
  unlist() %>% 
  median() #0.101 new 0.156

pct_below_building_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.07, 0.12] new 50% HDI: [0.07, 0.18]

pct_below_building_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.04, 0.18] new 5% HDI: [0.03, 0.37]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
plan(multisession)

pct_below_comm_tower_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  median() #.5584 new 0.6135

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.53, 0.59] new 50% HDI: [0.56, 0.66]

pct_below_comm_tower_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.46, 0.64] new 95% HDI: [0.46, 0.77]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
plan(multisession)

pct_below_wind_threshold <- future_map2(.x = rstan::extract(original_results, pars = c("shape"))[[1]], 
            .y = rstan::extract(original_results, pars = c("rate"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold %>% 
  unlist() %>% 
  median() #0.2723 new 0.2919

pct_below_wind_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.29] new 50% HDI: [0.28, 0.32]

pct_below_wind_threshold %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.21, 0.32] new 95% HDI: [0.22, 0.34]
```