---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Fall is index 1, spring 2

```{r}
season_results <- readRDS(here("bayesian_modeling", "gamma_season_stan.rds"))
```

Mode
```{r}
# mode (calculated from samples)
# fall
mode_draws_fall <- ((rstan::extract(season_results, "shape_fall")[[1]] - 1)/rstan::extract(season_results, "rate_fall")[[1]])*2183.475

median(mode_draws_fall)
#32.2696

hdi(mode_draws_fall, ci = 0.95)
#5% HDI: [-115.25, 172.58]

#spring
mode_draws_spring <- ((rstan::extract(season_results, "shape_spring")[[1]] - 1)/rstan::extract(season_results, "rate_spring")[[1]])*2183.475

median(mode_draws_spring)
#83.63531

hdi(mode_draws_spring, ci = 0.95)
#95% HDI: [-112.63, 251.79]
```

Median
```{r}
#fall
plan(multisession)

median_draws_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_fall %>% 
  unlist() %>% 
  median() # 223.2481

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [191.85, 247.62]

median_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) # 95% HDI: [143.58, 304.50]

# spring
plan(multisession)

median_draws_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_spring %>% 
  unlist() %>% 
  median() #319.1291

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [281.92, 356.19]

median_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [212.97, 429.43]
```

Mean
```{r}
#fall
plan(multisession)

mean_draws_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_fall %>% 
  unlist() %>% 
  median() #309.7425

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [277.12, 330.85]

mean_draws_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [235.24, 391.52]

#spring
plan(multisession)

mean_draws_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_spring %>% 
  unlist() %>% 
  median() #427.2789

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [386.09, 458.83]

mean_draws_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #5% HDI: [325.84, 543.71]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#fall
plan(multisession)

pct_below_radar_threshold_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  median() #0.3737

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) # 50% HDI: [0.33, 0.43]

pct_below_radar_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.23, 0.52]

#spring
plan(multisession)

pct_below_radar_threshold_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  median() #0.2586

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.30]

pct_below_radar_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.13, 0.40]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#fall
plan(multisession)

pct_below_building_threshold_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  median() #0.1198

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.07, 0.14]

pct_below_building_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.03, 0.23]

#spring
plan(multisession)

pct_below_building_threshold_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  median() #0.069

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.03, 0.08]

pct_below_building_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.01, 0.16]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#fall
plan(multisession)

pct_below_comm_tower_threshold_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  median() #0.6204

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.59, 0.67]

pct_below_comm_tower_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.50, 0.73]

#spring
plan(multisession)

pct_below_comm_tower_threshold_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  median() #0.4819

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.44, 0.53]

pct_below_comm_tower_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.35, 0.61]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#fall
plan(multisession)

pct_below_wind_threshold_fall <- future_map2(.x = rstan::extract(season_results, "shape_fall")[[1]], 
            .y = rstan::extract(season_results, "rate_fall")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  median() #0.3067

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.29, 0.34]

pct_below_wind_threshold_fall %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.23, 0.37]

#spring
plan(multisession)

pct_below_wind_threshold_spring <- future_map2(.x = rstan::extract(season_results, "shape_spring")[[1]], 
            .y = rstan::extract(season_results, "rate_spring")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  median() #0.2276

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.21, 0.26]

pct_below_wind_threshold_spring %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.14, 0.30]
```

Quantify the likelihood that one seasonal mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_spring) > unlist(mean_draws_fall))*100/length(unlist(mean_draws_spring))
#95.91667% probability that the spring mean is higher than the fall mean
```

