---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Adult is index 1, Juvenile 2
```{r}
age_results <- readRDS(here("bayesian_modeling", "gamma_age_stan.rds"))
```

Mode
```{r}
# mode (calculated from samples)
# adult
mode_draws_adult <- ((rstan::extract(age_results, "shape_adult")[[1]] - 1)/rstan::extract(age_results, "rate_adult")[[1]])*2183.475

median(mode_draws_adult)
#66.28403
hdi(mode_draws_adult, ci = 0.95) 
#95% HDI: [-134.84, 235.49]

# juv
mode_draws_juv <- ((rstan::extract(age_results, "shape_juv")[[1]] - 1)/rstan::extract(age_results, "rate_juv")[[1]])*2183.475

median(mode_draws_juv)
#74.72909

hdi(mode_draws_juv, ci = 0.95) 
#95% HDI: [-72.11, 205.35]
```

Median
```{r}
# adult
plan(multisession)

median_draws_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_adult %>% 
  unlist() %>% 
  median() # 293.2462

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [253.50, 327.98]

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [186.31, 403.19]

# juv
plan(multisession)

median_draws_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_juv %>% 
  unlist() %>% 
  median() #257.9696

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [228.51, 285.64]

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [176.60, 341.57]
```

Mean
```{r}
# adult
plan(multisession)

mean_draws_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_adult %>% 
  unlist() %>% 
  median() # 397.6275

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [359.05, 432.91]

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [293.12, 511.15]

# juv
plan(multisession)

mean_draws_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_juv %>% 
  unlist() %>% 
  median() #342.3979

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [313.68, 368.45]

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #5% HDI: [265.92, 426.39]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
# adult
plan(multisession)

pct_below_radar_threshold_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  median() #0.28595

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.23, 0.34]

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.15, 0.44]

# juv
plan(multisession)

pct_below_radar_threshold_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  median() #0.316

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.27, 0.36]

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.18, 0.45]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
# adult
plan(multisession)

pct_below_building_threshold_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  median() #0.0808

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.01, 0.19]

# juv
plan(multisession)

pct_below_building_threshold_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  median() #0.085

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.02, 0.18]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
# adult
plan(multisession)

pct_below_comm_tower_threshold_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  median() # 0.5152

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.47, 0.57]

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.37, 0.65]

# juv
plan(multisession)

pct_below_comm_tower_threshold_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  median() #0.5693

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.53, 0.61]

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.45, 0.69]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
# adult
plan(multisession)

pct_below_wind_threshold_adult <- future_map2(.x = rstan::extract(age_results, "shape_adult")[[1]], 
            .y = rstan::extract(age_results, "rate_adult")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  median() #0.2464

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.22, 0.28]

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.16, 0.32]

# juv
plan(multisession)

pct_below_wind_threshold_juv <- future_map2(.x = rstan::extract(age_results, "shape_juv")[[1]], 
            .y = rstan::extract(age_results, "rate_juv")[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  median() #0.2772

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.31]

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.19, 0.35]
```

Quantify the likelihood that one age mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_adult) > unlist(mean_draws_juv))*100/length(unlist(mean_draws_adult))
#79.25667% probability that the adult mean is higher than the juvenile mean
```