---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(jagsUI)
library(here)
library(furrr)
library(bayestestR)
```

Adult is index 1, Juvenile 2
```{r}
season_results <- readRDS(here("bayesian_modeling", "gamma_age.rds"))
```

Mode
```{r}
# mode (calculated from samples)
# fall
mode_draws_adult <- ((season_results$sims.list$shape_flight[,1] - 1)/season_results$sims.list$rate_flight[,1])*2183.475

median(mode_draws_adult)
#67.95292
hdi(mode_draws_adult, ci = 0.95) 
#95% HDI: [-148.09, 237.04]

#spring
mode_draws_juv <- ((season_results$sims.list$shape_flight[,2] - 1)/season_results$sims.list$rate_flight[,2])*2183.475

median(mode_draws_juv)
#78.28309

hdi(mode_draws_juv, ci = 0.95) 
#95% HDI: [-67.10, 208.14]
```

Median
```{r}
#fall
plan(multisession)

median_draws_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_adult %>% 
  unlist() %>% 
  median() # 294.4034

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [256.21, 334.35]

median_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [180.84, 402.95]

# spring
plan(multisession)

median_draws_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

plan(sequential)

median_draws_juv %>% 
  unlist() %>% 
  median() #259.5714

# median_draws_juv %>% 
#   unlist() %>% 
#   sd() #42.31298

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [228.68, 286.59]

median_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [178.69, 341.86]
```

Mean
```{r}
#fall
plan(multisession)

mean_draws_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_adult %>% 
  unlist() %>% 
  median() # 397.1969

# mean_draws_adult %>% 
#   unlist() %>% 
#   sd() #56.15242

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [354.76, 430.97]

mean_draws_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [295.41, 508.93]

#spring
plan(multisession)

mean_draws_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

plan(sequential)

mean_draws_juv %>% 
  unlist() %>% 
  median() #342.6243

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [313.26, 367.00]

mean_draws_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [265.66, 425.24]
```

Are these birds regularly flying lower than the flight heights reported via radar?
Calculate the percentage of these locations that fall below the minimum	threshold in Horton et al. 2016 (155m)
```{r}
#fall
plan(multisession)

pct_below_radar_threshold_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  median() #0.2836

# pct_below_radar_threshold_adult %>% 
#   unlist() %>% 
#   sd() #0.07868222

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.22, 0.33]

pct_below_radar_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.14, 0.45]

#spring
plan(multisession)

pct_below_radar_threshold_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              return(sum(res < 155)/10000)
            })

plan(sequential)

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  median() #0.3126

# pct_below_radar_threshold_juv %>% 
#   unlist() %>% 
#   sd() #0.0705226

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.36]

pct_below_radar_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.18, 0.45]
```

How may of these locations are at an altitude where they might collide with a building (0-47m)?
```{r}
#fall
plan(multisession)

pct_below_building_threshold_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  median() #0.0796

# pct_below_building_threshold_adult %>% 
#   unlist() %>% 
#   sd() #0.05163886

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.01, 0.20]

#spring
plan(multisession)

pct_below_building_threshold_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 47)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  median() #0.0827

# pct_below_building_threshold_juv %>% 
#   unlist() %>% 
#   sd() #0.04471384

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.04, 0.10]

pct_below_building_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.02, 0.18]
```

How may of these locations are at an altitude where they might collide with a comm tower (0-305m)?
```{r}
#fall
plan(multisession)

pct_below_comm_tower_threshold_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  median() # 0.514

# pct_below_comm_tower_threshold_adult %>% 
#   unlist() %>% 
#   sd() #0.07755391

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.46, 0.56]

pct_below_comm_tower_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.38, 0.66]

#spring
plan(multisession)

pct_below_comm_tower_threshold_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res <= 305)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  median() #0.5675

# pct_below_comm_tower_threshold_juv %>% 
#   unlist() %>% 
#   sd() #0.06716926

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.53, 0.61]

pct_below_comm_tower_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.45, 0.68]
```

How may of these locations are at an altitude where they might collide with a wind turbine (32.2-163.8m)?
```{r}
#fall
plan(multisession)

pct_below_wind_threshold_adult <- future_map2(.x = season_results$sims.list$shape_flight[,1], 
            .y = season_results$sims.list$rate_flight[,1],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  median() #0.2456

# pct_below_wind_threshold_adult %>% 
#   unlist() %>% 
#   sd() #0.04276762

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.23, 0.28]

pct_below_wind_threshold_adult %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.16, 0.32]

#spring
plan(multisession)

pct_below_wind_threshold_juv <- future_map2(.x = season_results$sims.list$shape_flight[,2], 
            .y = season_results$sims.list$rate_flight[,2],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rgamma(n = 10000, 
                          shape = x,
                          rate = y)
              
              res <- res * 2183.475
              
              derived <- sum(res > 32.2 & res <= 163.8)/10000
              
              return(derived)
            })

plan(sequential)

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  median() #0.2759

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.5) #50% HDI: [0.26, 0.31]

pct_below_wind_threshold_juv %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [0.19, 0.35]
```

Quantify the likelihood that one age mean is greater than the other
This is called probability of superiority: see "A Probability-Based Measure of Effect Size: Robustness to Base Rates and Other Factors"
```{r}
sum(unlist(mean_draws_adult) > unlist(mean_draws_juv))*100/length(unlist(mean_draws_adult))
#78.67316% probability that the adult mean is higher than the juvenile mean
```