---
title: "R Notebook"
output: html_notebook
---

Measuring the sensitivity of our analysis to violations of our assumption that all diurnal locations are ground locations.

Prep code (same as original model)
```{r}
library(tidyverse)
library(sf)
library(suncalc)
library(here)
library(rstan)
library(shinystan)
library(truncnorm)
library(furrr)
library(bayestestR)

options(mc.cores = 4)
plan(multisession)

covariates <- read.csv(here("intermediate_files", "imported_movebank_data.csv"))

raw_data <- st_read(here("intermediate_files", "raw_elevation_values.shp")) %>% 
  st_drop_geometry() %>% 
  arrange(Field1) %>% 
  dplyr::select(t_hae_m)

raw_data <- covariates %>% 
  bind_cols(raw_data)

#calculate height above terrain and begin filtering to 3D fixes
raw_data <- raw_data %>% 
  mutate(height_above_terrain = height_above_wgs84 - t_hae_m) %>% 
  filter(fix == "3D") %>% 
  filter(point_state != "") #filter out empty point states

# hist(raw_data$height_above_terrain)
# summary(raw_data$height_above_terrain)

# determine whether each is a day or a night location
raw_data <- raw_data %>% 
  mutate(time_lubr = ymd_hms(time)) %>% 
  filter(!is.na(time_lubr))#discarding 118

raw_data %>%
  dplyr::transmute(date = as.Date(time_lubr), lat = lat, lon = lon) %>%
  getSunlightTimes(data = .) %>%
  pull(sunrise) -> 
  raw_data$sunrise

raw_data %>%
  dplyr::transmute(date = as.Date(time_lubr), lat = lat, lon = lon) %>%
  getSunlightTimes(data = .) %>%
  pull(sunset) -> 
  raw_data$sunset

raw_data %>%
  mutate(day_night = if_else(time_lubr > sunrise & time_lubr < sunset, "Day", "Night")) ->
  raw_data

raw_data %>% 
  group_by(day_night) %>% 
  tally()

# possible flight location if a) the bird is migrating, b) the point is nocturnal, 
# c) the point demonstrates some movement between prior and subsequent points (6.6 km)
# this also implies that tracks cannot begin or end on a flight location. Given the small number of these in our
# dataset, I'm okay with that assumption for now

altitude_data <- raw_data %>% 
  mutate(probable_ground = if_else(day_night == "Day", 1, NA)) %>% 
  mutate(possible_flight = if_else(point_state %in% c("Point state: Migratory (spring)", "Point state: Migratory (fall)") & day_night == "Night" & moving == TRUE, 1, NA))

altitude_data %>% 
  group_by(possible_flight) %>% 
  tally() #258, down from 428 possible flight locations

# plot results
altitude_data %>%
  filter(probable_ground == 1) %>%
  pull(height_above_terrain) %>%
  hist(main = "Presumed ground locations", breaks = 120, xlim = c(0,100))

altitude_data %>%
  filter(possible_flight == 1) %>%
  pull(height_above_terrain) %>%
  hist(main = "Possible flight locations")

#splitting into two dataframes
known_ground_df <- altitude_data %>% 
  filter(probable_ground == 1)

unknown_df <- altitude_data %>% 
  filter(possible_flight == 1)
```

Setting 2% of locations (Rabe et al. 1983) to be diurnal flight locations, with altitudes generated from a uniform distribution between 0 and 21.5m
```{r}
# unknown flight locations
unknown_df <- unknown_df %>% 
  mutate(hat_scaled = height_above_terrain/2183.475) # Scale locations between -1 and 1

# known ground locations
known_ground_df$diurnal_flight_altitude <- runif(n = nrow(known_ground_df), max = 21.5)

known_ground_df$index <- 1:nrow(known_ground_df)

to_sample <- sample(1:nrow(known_ground_df), 0.02*nrow(known_ground_df))

known_ground_df <- known_ground_df %>% 
  mutate(height_above_terrain = if_else(index %in% to_sample, height_above_terrain + diurnal_flight_altitude, height_above_terrain)) %>% # if this location is part of the 2%, add the diurnal flight altitude to the true altitude
   mutate(hat_scaled = height_above_terrain/2183.475)
```


```{r}
init <- function(){list(nu_obs = rgamma(1,2,0.1),
                        mu_obs = rnorm(1,0,0.2),
                        sigma_obs = runif(1,0,0.2),
                        mu_alt = runif(1,-1,1),
                        sigma_alt = runif(1,0,1),
                        flight_prior = rbeta(1,2,2))}

model_compiled <- stan_model(here("modeling", "stan", "lnorm_original.stan"))

fit <- sampling(model_compiled, data = list(n_obs_known = nrow(known_ground_df),
                                            HAT_known = known_ground_df$hat_scaled,
                                            n_obs_unknown = nrow(unknown_df),
                                            HAT_unknown = unknown_df$hat_scaled), 
                init = init,
                pars = c("nu_obs","mu_obs", "sigma_obs", "mu_alt", "sigma_alt", "flight_prior", "p_flight"), #, "HAT_known_mean_gte", "HAT_known_sd_gte", "HAT_known_ppc", "HAT_unknown_ppc"
                iter = 15000,
                #control = list(adapt_delta = 0.99), #, max_treedepth = 20
                chains = 4, 
                init_r = 0,
                seed = 8)

print(fit)
traceplot(fit, pars = c("mu_obs", "sigma_obs", "mu_alt", "sigma_alt", "flight_prior"))

saveRDS(fit, file = here("sensitivity_analysis", "lnorm_sensitivity.rds"))
```

Calculating comparative statistics

Median
```{r}
median_draws <- future_map2(.x = rstan::extract(fit, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(fit, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(median(res))
            })

median_draws %>% 
  unlist() %>% 
  median() #262.9985

median_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [219.75, 309.09]
```

Mean
```{r}
mean_draws <- future_map2(.x = rstan::extract(fit, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(fit, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(mean(res))
            })

mean_draws %>% 
  unlist() %>% 
  median() # 379.7752

mean_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [318.26, 448.68]
```

Standard deviation
```{r}
sd_draws <- future_map2(.x = rstan::extract(fit, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(fit, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(sd(res))
            })

sd_draws %>% 
  unlist() %>% 
  median() # 394.1858

sd_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) # 95% HDI: [280.45, 540.98]
```

Skewness
```{r}
skew_draws <- future_map2(.x = rstan::extract(fit, pars = c("mu_alt"))[[1]], 
            .y = rstan::extract(fit, pars = c("sigma_alt"))[[1]],
            .progress = TRUE,
            .options = furrr_options(seed = 8),
            .f = function(x, y){
              res <- rlnorm(n = 10000, 
                          meanlog = x,
                          sdlog = y)
              
              res <- res * 2183.475
              
              return(EnvStats::skewness(res))
            })

skew_draws %>% 
  unlist() %>% 
  median() # 3.960762

skew_draws %>% 
  unlist() %>% 
  hdi(ci = 0.95) #95% HDI: [2.62, 6.49]
```
